Validation of an Actuator Line Model Coupled to a Dynamic Stall Model for Pitching Motions Characteristic to Vertical Axis Turbines

### 2016-06-11 paper.tex
Turn off DSM test and figures improvement with GNUPLOT

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CN226revolutions.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CT226revolutions.eps}
\end{minipage} 
\caption{\label{revolutions}Normal (left) and tangential (right) force coefficients varying the number of revolutions for a pitching motion of NACA0021 airfoil with a maximum amplitude of 22.6$\degree$.}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CNmesh.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CTmesh.eps}
\end{minipage} 
\caption{\label{figmesh}Normal (left) and tangential (right) force coefficients varying the size of the reference mesh for a pitching motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CN226dtLEScoarse.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CT226dtLEScoarse.eps}
\end{minipage} 
\caption{\label{figdtcoarse}Normal (left) and tangential (right) force coefficients varying time-step discretization for a pithing motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CN138.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CT138.eps}
\end{minipage} 
\caption{\label{fig138}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 13.8\degree\ (analog to $\lambda = 4.19$).}
\end{figure}

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CN174.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CT174.eps}
\end{minipage} 
\caption{\label{fig174}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 17.4\degree\ (analog to $\lambda = 3.34$).}
\end{figure}

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CN226.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CT226.eps}
\end{minipage} 
\caption{\label{fig226}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 22.6\degree\ (analog to $\lambda = 2.60$).}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CNRANSLES.eps}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\includegraphics[width=\columnwidth]{CTRANSLES.eps}
\end{minipage} 
\caption{\label{RANSLES}Normal (left) and tangential (right) force coefficients varying the size of the reference mesh, pithing motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

>>>>

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CN226revolutions}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CT226revolutions}}
\end{minipage} 
\caption{\label{revolutions}Normal (left) and tangential (right) force coefficients varying the number of revolutions for a pitching motion of NACA0021 airfoil with a maximum amplitude of 22.6$\degree$.}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNmesh}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTmesh}}
\end{minipage} 
\caption{\label{figmesh}Normal (left) and tangential (right) force coefficients varying the size of the reference mesh for a pitching motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CN226dtLEScoarse}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CT226dtLEScoarse}}
\end{minipage} 
\caption{\label{figdtcoarse}Normal (left) and tangential (right) force coefficients varying time-step discretization for a pithing motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CN138}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CT138}}
\end{minipage} 
\caption{\label{fig138}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 13.8\degree\ (analog to $\lambda = 4.19$).}
\end{figure}

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CN174}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CT174}}
\end{minipage} 
\caption{\label{fig174}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 17.4\degree\ (analog to $\lambda = 3.34$).}
\end{figure}

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CN226}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CT226}}
\end{minipage} 
\caption{\label{fig226}Normal (left) and tangential (right) force coefficients during pitching motions of NACA0021 airfoil with a maximum amplitude of 22.6\degree\ (analog to $\lambda = 2.60$).}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNRANSLES}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTRANSLES}}
\end{minipage} 
\caption{\label{RANSLES}Normal (left) and tangential (right) force coefficients for different turbulence models, pithing motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

\subsection{Unsteady effects correction}
A test for the simulation with the DSM turned off was carried out, it means there is no compensation for the unsteady effects: the effective angle of attack is the angle of attack provided by the ALM. Figure \ref{AMP174corrections} depicts that simulated results are closer to experimental data with the corrections. Both $C_N$ and $C_T$ peak values are not overestimated. The $C_N$ loop, shows that the model without the corrections was not able to capture reattachment flow effects.

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNAMP174corrections}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTAMP174corrections}}
\end{minipage} 
\caption{\label{AMP174corrections}Normal (left) and tangential (right) force coefficients with and without unsteady effects correction, pithing motion with a maximum amplitude of 17.4\degree\ }
\end{figure}
